The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-09 paper/main.tex
Added some CTS2 text.
Updates to sql and paper.

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\setlength\parindent{0pt}

@@

\begin{algorithmic}
\While{$i < 1000$} 
\State $i \gets i + 1$
\State $word \gets random(word\_list)$
\State $repos \gets git\_search(word)$
\State $j \gets random(0...size(repos))$
\State $repo \gets repos_j$
\State \Call{process}{repo}
\EndWhile
\end{algorithmic}\footnote

$\displaystyle\frac{\sum\limits_{i=1}^{n} f( \left\{{i_j,i_{j+1},...,i_{j+k}  }\right\} ) } {n} $.

@@

\subsection{Summary Statistics}
\begin{table}[!ht]
\begin{center}
\caption{GitHub Summary Statistics}
\begin{tabular}{rrrrrrr}
\hline
Variable & Mean & Min & Max & Std. Dev. \\
\hline
\input{summary_statistics}
\hline
\end{tabular}
N = 100 Repositories
\end{center}
\end{table}

\subsection{Hypotheses}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}

\emph{Hypothesis 2: As the number Repository Forks increase, the Issue Resolution Time will decrease.}\\
\includegraphics[height=3in,width=3in]{images/issue_close_time_forks_scatterplot.png}

\emph{Hypothesis 3: There will be more Issue Reporters than Committers by an order of magnitude.}\\
\includegraphics[height=3in,width=3in]{images/issue_reporters_histogram.png}
\includegraphics[height=3in,width=3in]{images/committers_histogram.png}
\includegraphics[height=3in,width=3in]{images/issue_reporters_committers_scatterplot.png}

\subsection{Research Questions}
\emph{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\

@@

\emph{Research Question 3: Can GitHub be used for more that code artifacts?}\\

>>>>

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\MakeRobust{\Call}
\setlength\parindent{0pt}

@@

\begin{algorithmic}
\While{$i < 1000$} 
\State $i \gets i + 1$
\State $word \gets random(word\_list)$
\State $repos \gets git\_search(word)$
\State $j \gets \Call{random}{0... \Call{size}{repos}}$
\State $repo \gets repos_j$
\State \Call{store}{repo}
\EndWhile
\end{algorithmic}

The \textsc{store} function accepts as an input a given random repository. The purpose of this function is to persist the given repository to a database for further analysis.

\begin{figure}
\includegraphics[height=3in,width=3in]{images/er.png}
\caption{GitHub Date Entity Relationship diagram}
\end{figure}

$\displaystyle\frac{\sum\limits_{i=1}^{n} f(  S_{ij} ) } {n} $.

@@

\subsection{Summary Statistics}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{rrrrrrr}
\hline
Variable & Mean & Min & Max & Std. Dev. \\
\hline
\input{summary_statistics}
\hline
\end{tabular}
N = 100 Repositories
\caption{GitHub Summary Statistics}
\end{center}
\end{table}

\subsection{Hypotheses}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\begin{figure}
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}
\caption{Repostitory watchers and forks}
\end{figure}

\emph{Hypothesis 2: As the number Repository Forks increase, the Issue Resolution Time will decrease.}\\
\begin{figure}
\includegraphics[height=3in,width=3in]{images/issue_close_time_forks_scatterplot.png}
\caption{Repostitory issue close time and number of forks}
\end{figure}

\emph{Hypothesis 3: There will be more Issue Reporters than Committers by an order of magnitude.}\\
\begin{figure}
\includegraphics[height=3in,width=3in]{images/issue_reporters_histogram.png}
\caption{Repostitory issue reporters}
\end{figure}
\begin{figure}
\includegraphics[height=3in,width=3in]{images/committers_histogram.png}
\caption{Repostitory committers}
\end{figure}
\begin{figure}
\includegraphics[height=3in,width=3in]{images/issue_reporters_committers_scatterplot.png}
\caption{Repostitory issue reporters and committers}
\end{figure}

\subsection{Research Questions}
\emph{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
\begin{figure}
\includegraphics[height=3in,width=3in]{images/committers_percentage_pie_chart.png}
\caption{Individual committer commit percentage per repository}
\end{figure}

@@

\emph{Research Question 3: Can GitHub be used for more that code artifacts?}\\
As part of the OMG\textregistered standardization process, the CTS2 Specification used GitHub issue tracker to track specification changes.
